### 2018-08-07 paper/security-discussion.tex
WIP on UC simulator argument

The second change is that we use several nodes per layer as opposed to only 
one.
The proofs of Sphinx rest on the results of \textcite{CLOnionRouting}, which 
are results for ordinary \ac{OR} with only one node per layer.
\sonja{Daniel is working on sketching a proof/rephrasing the following.}
As long as we output all the nodes in the next layer, the proofs should not 
change.
We note that this is actually quite natural as a malicious adversary can drop 
any incoming traffic to a router and wait for the timeout and retransmission to 
the next node.
As such, the adversary can learn all nodes in the layer.

>>>>

The second change is that we use several nodes per layer as opposed to only 
one.
The proofs of Sphinx rest on the results of \textcite{CLOnionRouting}, which 
are results for traditional \ac{OR} with only one node per layer.
We must thus ensure that the proofs of \citeauthor{CLOnionRouting} also holds 
for sets of nodes.

Analogously to traditional \ac{OR}, we also reveal the previous and next sets 
of nodes to the adversary.
We note that this is actually quite natural as a malicious adversary can drop 
any incoming traffic to a router and wait for the retransmission, \ie when the 
node has selected a new node from the next layer and retried sending.
As such, the adversary can learn all nodes in the layer --- just as for 
traditional \ac{OR}.
